---
title: "beepboop"
author: "Sarah Hamilton and Maggie Hammond"
date: "4/17/2022"
output:   
  html_document:
    theme: flatly
    code_folding: hide
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(here)
library(janitor)
library(equatiomatic)
library(broom)
library(ggpubr)
```

```{r}
water_markets <- read_csv(here("data", "Water_Districts.csv")) %>% 
  clean_names()
```

# Plot Marginal Cost Data

```{r}
# linear regression will be the estimate of the marginal abatement cost curve

districts <- water_markets %>% 
  select(-x1) %>% 
  pivot_longer(cols = c(mc_kern, mc_mojave, mc_antelope, mc_ventura),
               names_to = 'county',
               values_to = 'mc') %>% 
  mutate(county = case_when(
    county == 'mc_kern' ~ 'Kern',
    county == 'mc_ventura' ~ 'Ventura',
    county == 'mc_antelope' ~ 'Antelope',
    county == 'mc_mojave' ~ 'Mojave'
  ))

ggplot(data = districts, aes(y = mc, x = reduction)) +
  geom_point(aes(color = county)) +
  scale_color_manual(values = c('orange', 'red', 'green', 'purple')) +
  labs(x = "Reduction in Water (AF)",
       y = "Marginal Cost ($/AF)",
       color = "County",
       title = "Marginal Cost of Water \n Reduction in Central California") +
  theme_minimal()
  # geom_smooth(method = "lm")
```


# Create Marginal Abatement Cost Linear Regression Model 

```{r}
#penguin_lm <- lm(body_mass_g ~ flipper_length_mm, data = penguins)

mojave_lm <- lm(mc_mojave ~ reduction, data = water_markets) 

ventura_lm <- lm(mc_ventura ~ reduction, data = water_markets) 

antelope_lm <- lm(mc_antelope ~ reduction, data = water_markets)

kern_lm <- lm(mc_kern ~ reduction, data = water_markets)

# extract the equations for marginal cost of abatement 

extract_eq(model = mojave_lm, use_coefs = TRUE)
extract_eq(model = ventura_lm, use_coefs = TRUE)
extract_eq(model = antelope_lm, use_coefs = TRUE)
extract_eq(model = kern_lm, use_coefs = TRUE)

# total_function <- function(x){-0.593+1.61*x}


```

# Derive District's Demand Curves for Water

Abatement = Eo - E

```{r}
mojave_mb <- function(x){534.11-3.83*x}
ventura_mb <- function(x){437.65-1.79*x}
antelope_mb <- function(x){629.14-2.86*x}
kern_mb <- function(x){341.24-2.25*x}

### OUTPUT THESE EQUATIONS SOMEHOW****


ggplot(data.frame(x = c(0,250)), aes(x = x)) +
  stat_function(fun = mojave_mb, color = "green") +
  stat_function(fun = ventura_mb, color = "purple") +
  stat_function(fun = antelope_mb, color = "orange") +
  stat_function(fun = kern_mb, color = "red") +
  theme_minimal() +
  ylim(0, 750) +
  labs(x = "Amount of Water Used (AF)", y = "Price of Water ($/AF)",
       title = "Demand for Water") 
  
  # scale_color_manual(name = 'District',
  #                    breaks = c('Mojave','Ventura','Antelope','Kern'),
  #                    values = c('Mojave' = "#008080", 'Ventura' = "#ff7373", 'Antelope' = "#528360", 'Kern' ="#7d84ad"))
  
  # legend(175, 600, legend = c("Mojave", "Ventura", "Antelope", "Kern"), col = c("#008080", "#ff7373", "#528360", "#7d84ad"), lty = 1:2, cex = 0.8)
```

Based on the districts' demand curves, Antelope is willing to pay the most for the first acre foot of water because their marginal benefit for their first unit of water is the highest (around 600).

# Policy Analysis

# Policy 1: Cap Without Trade


# Policy 2: Tax on Water Use


# Policy 3: Cap and Trade 

```{r}
water_markets_sum <- water_markets %>%
  mutate(total_water = mc_kern+mc_mojave+mc_antelope+mc_ventura)

total_lm <- lm(total_water ~ reduction, data = water_markets_sum)

extract_eq(model = total_lm, use_coefs = TRUE)


districts <- water_markets_sum %>% 
  select(-x1) %>% 
  pivot_longer(cols = c(mc_kern, mc_mojave, mc_antelope, mc_ventura, total_water),
               names_to = 'county',
               values_to = 'mc') %>% 
  mutate(county = case_when(
    county == 'mc_kern' ~ 'Kern',
    county == 'mc_ventura' ~ 'Ventura',
    county == 'mc_antelope' ~ 'Antelope',
    county == 'mc_mojave' ~ 'Mojave',
    county == 'total_water' ~ 'Total'
  ))

ggplot(data = districts, aes(y = mc, x = reduction)) +
  geom_point(aes(color = county)) +
  scale_color_manual(values = c('orange', 'red', 'green', 'purple', 'yellow')) +
  labs(x = "Reduction in Water (AF)",
       y = "Marginal Cost ($/AF)",
       color = "County",
       title = "Marginal Cost of Water \n Reduction in Central California") +
  theme_minimal()
  # geom_smooth(method = "lm")

```

